PhotoD: LSST photometric distances out to 100 kpc.

### 2023-11-08 paper/methodology.tex
Minor edits to the text.

\begin{figure}[ht!]
	\plotone{GOOZvV.png}
	\caption{Color-color diagram. \magcom{Add a version with overlaid evolutionary tracks in order to emphasize the required precision of the photometry required to disentangle the dwarfs and giants and different metallicities. \textbf{Are ev. tracks with different metallicities overlapping}? Can there be a situation where there is confusion between giants and dwarfs with different metallicities?} \label{fig:2c_example}}
\end{figure}

@@

\begin{figure}[ht!]
	\plotone{Fdtez8.png}
	\caption{Yadayada. \label{fig:metallicity}}
\end{figure}

@@

\begin{figure}[ht!]
	\plotone{BYiR7o.png}
	\caption{Extinction \& degeneracies. \label{fig:degeneracies}}
\end{figure}

Another important degeneracy arises from the fact that even for a fixed \teff and \mh, the \logg and thus the luminosity are not uniquely determined by the colors: a degeneracy may exist between the giant branch and the main sequence as the colors constructed from \textit{ugrizy} bands are not sensitive to \logg (\magcom{As evident from ŽI's gr-ri plot.}). We treat this issue by adopting a prior based on bins in apparent magnitude.

We adopt a Bayesian framework in which we simultaneously fit for \Mb, \mh and \Ar, assuming a fixed \RV value of 3.1\footnote{In principle \RV could be also fitted for.} The posterior for each individual star with LSST photometry is then given as:

\begin{equation} \label{eq:likelihood}
	\begin{split}
		    &\Pcond{\Mb, \, \mh, \, \Ar}{\vec{c}} = \\
		& \frac{\Pcond{\vec{c}}{\Mb, \, \mh, \, \Ar} P\arg{\Mb, \, \mh, \, \Ar}}{P\arg{\vec{c}}} \,
	\end{split}
\end{equation}

@@

\begin{equation}
	ln \mathcal{L} = {-1 \over \sqrt{2\pi}} \,\sum_{i=1}^N \left({ c^{obs}_i - c^{mod}_i  \over \sigma_i } \right)^2 \,
\end{equation}

@@

% -- modeli za boje moraju biti savršeni
% -- novi prior iz trilegala
% -- robustni framework koji može obraditi 10B zvijezda, i da nije spor
% -- probali smo s MCMC, exhaustive locus search, i neuronske mreže koje su bile najbrže (drugi članak)

%$L=4\pi\sigma R^2 T^4=4\pi \sigma \frac{GM}{g} T^4$\\
%$g = \frac{GM}{R^2}$\\
%$\mu = m_b - M_b {\ }(+ A_b)$\\
%$log(d) = 1 + \frac{\mu}{5}$\\

>>>>

@@

@@

Another important degeneracy arises from the fact that even for a fixed \teff and \feh, the \logg and thus the luminosity are not uniquely determined by the colors: a degeneracy may exist between the giant branch and the main sequence as the colors constructed from \textit{ugrizy} bands are not sensitive to \logg (\magcom{As evident from ŽI's gr-ri plot.}). We treat this issue by adopting a prior based on bins in apparent magnitude.

We adopt a Bayesian framework in which we simultaneously fit for \Mb, \feh and \Ar, assuming a fixed \RV value of 3.1\footnote{In principle \RV could be also fitted for.} The posterior for each individual star with LSST photometry is then given as:

\begin{equation} \label{eq:likelihood}
	\begin{split}
		    &\Pcond{\Mb, \, \feh, \, \Ar}{\vec{c}} = \\
		& \frac{\Pcond{\vec{c}}{\Mb, \, \feh, \, \Ar} P\arg{\Mb, \, \feh, \, \Ar}}{P\arg{\vec{c}}} \,
	\end{split}
\end{equation}

@@

\begin{equation}
	ln (\mathcal{L}) = C - {1 \over 2} \,\sum_{i=1}^N \left({ c^{obs}_i - c^{mod}_i  \over \sigma_i } \right)^2 \,
\end{equation}

@@
